Verifying Demonstrations

### 2019-02-13 paper/intro.tex
Removes DB from related work in outline

The paper is organized as follows.
\Cref{system-model}, we describe our system model and summarize the desired 
properties for crowd counting.
We then discuss related work in terms of these properties in 
\cref{related-work}:
we first discuss the crowd counting methods that are classically used, then 
work on location proof systems and, finally, some work on distance bounding.

>>>>

The paper is organized as follows.
\Cref{system-model}, we describe our system model and summarize the desired 
properties for crowd counting.
We then discuss related work in terms of these properties in 
\cref{related-work}:
we first discuss the crowd counting methods that are classically used followed 
by work on location proof systems.
